\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=0.75in}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fontawesome} % For LinkedIn and GitHub icons
\usepackage{tabularx}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,
    urlcolor=black,
    citecolor=black
}

\titleformat{\section}{\large\bfseries}{}{0em}{}
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}
\renewcommand{\familydefault}{\sfdefault}  % Use a sans-serif font

\titlespacing*{\section}{0pt}{1em}{0.5em}
\titlespacing*{\subsection}{0pt}{0.75em}{0.5em}

\setlength{\parindent}{0pt}

\begin{document}

\begin{center}
    \Huge{\textbf{Omkar Sandip Koki}} \\[10pt]
    \normalsize
    \begin{tabular}{c}
        \href{https://github.com/omkarkokil}{\raisebox{-0.2\height}{\small\faGithub}\ omkarkokil} \ $|$ \ 
        \href{https://www.linkedin.com/in/omkar-kokil-384231285/}{\raisebox{-0.2\height}{\small\faLinkedin}\ Omkar Kokil} \ $|$ \ 
        \href{mailto:omkarkokil2709@gmail.com}{\raisebox{-0.2\height}{\small\faEnvelope}\ omkarkokil2709@gmail.com} \ $|$ \ 
        \href{tel:+91917219725697}{\raisebox{-0.2\height}{\small\faMobile}\ +91 917219725697}
    \end{tabular}
\end{center}

\vspace{0.5em}
\hrule
\vspace{1em}

\section*{Objective}
Passionate and dedicated software developer with a strong foundation in full-stack web development, currently pursuing a master’s degree. Experienced in building dynamic and responsive user interfaces using React.js and Next.js. Skilled in developing robust backend services with Node.js and designing efficient APIs using GraphQL. Enthusiastic about learning and implementing Docker containerization and AWS cloud services to enhance application deployment and scalability. Adept at problem-solving and working in collaborative environments. Strong focus on user experience and performance optimization. Committed to continuous learning and staying updated with the latest industry trends and technologies. Seeking opportunities as a React JS Developer to leverage expertise in frontend development and contribute to innovative projects.

\section*{Education}
\begin{itemize}[leftmargin=*]
    \item \textbf{Master in Computer Application} \\
    Pune University, 2023-2025
    \item \textbf{Bachelor’s in Computer Application} \\
    Shivaji University, 2020-2023
\end{itemize}

\section*{Professional Experience}
\begin{itemize}[leftmargin=*]
    \item \textbf{Jr Full Stack Developer (Onsite)} \\
    Argan IT Services, Pune Wakad \\
    November 2023 – Present
    \item \textbf{Full Stack Developer Intern (Remote)} \\
    Unicorniz Innovations, Andaman Nicobar Islands \\
    September 2023 – November 2023
\end{itemize}

\section*{Projects}
\begin{itemize}[leftmargin=*]
    \item \textbf{Chat Website in Next.js} \hfill \href{https://thunder-chat-navy.vercel.app/}{\small\faExternalLink\ Live Demo} \\
    Developed a real-time chat application using Next.js.
    \item \textbf{Ecommerce Website in MERN stack} \hfill \href{https://onestopshop-tzua.onrender.com/}{\small\faExternalLink\ Live Demo} \\
    Built a fully functional ecommerce platform.
    \item \textbf{Portfolio Website} \hfill \href{https://okdev.vercel.app/}{\small\faExternalLink\ Live Demo} \\
    Developed my portfolio website using React.js.
    \item \textbf{Blogging Website in MERN stack} \hfill \href{https://magicalwind.onrender.com/}{\small\faExternalLink\ Live Demo} \\
    Created a dynamic blogging platform.
\end{itemize}

\section*{Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{Problem Solving, Leading, Grit}
    \item \textbf{Languages:} JavaScript
    \item \textbf{Novice Languages:} C++, Python, Java
    \item \textbf{Frameworks:} React JS, Tailwind CSS, Next JS
    \item \textbf{Databases:} MySQL, MongoDB, Postgres
    \item \textbf{Technologies:} Git, Linux, Windows
\end{itemize}

\end{document}
